---
title: "Genomic Analysis Report"
author: "Dylan Lawless, PhD"
affiliation: "Department of Intensive Care and Neonatology, University Children's Hospital Zurich, University of Zurich"
output: html_document
---

```{r setup, include=FALSE}

# Define variables, you could also source an R script that outputs these variables
SampleID <- "XYZ_STUDY_D.XYZ003_DNA"
CodingVariant <- "ENST00000380588.4:c.53G>A"
ProteinVariant <- "ENSP00000369962.4:p.Trp18Ter"
ACMGScore <- 2
```

## Results
test
### Causal Variant Summary

- **Sample ID:** <span style="color:red;">`r SampleID`</span>
- **HGVSc coding variant:** <span style="color:red;">`r CodingVariant`</span>
- **Protein variant:** <span style="color:red;">`r ProteinVariant`</span>
- **ACMG score:** <span style="color:red;">`r ACMGScore`</span>

<!-- ![ACMGuru automated analysis...](../output/aggregate_variants_per_criteria.pdf) -->

```{r criteria-count-plot, echo=FALSE, message=FALSE, results='asis', fig.keep='all'}
# Source the script that generates the plot
# source("../tests/test_main_filter.R")
capture.output(source("../tests/test_main_filter.R"), file = NULL)


# If the plot is assigned to a variable but not explicitly printed in the sourced script, print it here
print(p.criteria_count_each_gene)
```


#### Causal Variant Evidence Interpretation

The analysis of variant interpretation performed by ACMGuru is summarised from the following evidence sources:

[This document's source code is available from the GitHub repository](https://github.com/DylanLawless/kit_assess/blob/master/latex/report.tex).

All code used in this report is available on the [GitHub repository](https://github.com/DylanLawless/kit_assess).
